Calendar-based graphics for visualising people's daily schedules

### 2017-07-13 main.Rmd
Added legend to overlaying plot and facet plot

## Overlaying subsets

The comparison of one sensor to another adds additional insights to the dataset, which is commonly done with an overlaying plot such as Figure \ref{fig:overlay}. For instance, the dominant patterns occurred to both train stations--Flinders Street Station and Flagstaff station--are together driven by the commuters on the work days; however, the former is overwhelmed by the number of pedestrians during the weekends and public holidays, compared to the latter. It suggests that Flagstaff station limits its functionality as simply the public transport hub for day-to-day commuters, but various activities take place around the Flinders Street Station other than commuting. Because Flinders Street Station closely lies to South Bank and other places of attractions where the locals go for leisure and the tourists for travelling. It can be noted from Figure \ref{fig:overlay} that State Library follows the similar temporal trend as Flinders Street Station on non-work days.

```{r overlay, fig.height = 6.5, fig.cap = "Superimposing line graphs of three sensors in the monthly calendar. The orange line and the purple line, represented by the number of pedestrians at Flagstaff Station and Flinders Street Station, are on top of the green one indicating State Library. Flagstaff station is not as busy as the other two on non-work days."}
```

The nighttime events, such as White Night and New Year Evening Firework, has barely affected the operation of Flagstaff Station but heavily affected the incoming and outgoing traffic to Flinders Street Station and State Library on these days.

>>>>

## Overlaying and faceting subsets

The comparison of one sensor to another adds additional insights to the dataset, which is commonly done with an overlaying plot such as Figure \ref{fig:overlay}. For instance, the dominant patterns occurred to both train stations--Flinders Street Station and Flagstaff station--are together driven by the commuters on the work days; however, the former is overwhelmed by the number of pedestrians during the weekends and public holidays, compared to the latter. It suggests that Flagstaff station limits its functionality as simply the public transport hub for day-to-day commuters, but various activities take place around the Flinders Street Station other than commuting. Because Flinders Street Station closely lies to South Bank and other places of attractions where the locals go for leisure and the tourists for travelling. It can be noted from Figure \ref{fig:overlay} that State Library follows the similar temporal trend as Flinders Street Station on non-work days. The nighttime events, such as White Night and New Year Evening Firework, has barely affected the operation of Flagstaff Station but heavily affected the incoming and outgoing traffic to Flinders Street Station and State Library on these days.

```{r overlay, fig.height = 7, fig.cap = "Overlaying line graphs of the 3 sensors in the monthly calendar. Flagstaff station is not as busy as the other two on non-work days."}
```

As

```{r facet, fig.height = 11, fig.cap = "Line graphs faceted by the 3 sensors in the monthly calendar."}
```

### 2017-07-13 main.tex
Added legend to overlaying plot and facet plot

\subsection{Overlaying subsets}\label{overlaying-subsets}

The comparison of one sensor to another adds additional insights to the
dataset, which is commonly done with an overlaying plot such as Figure
\ref{fig:overlay}. For instance, the dominant patterns occurred to both
train stations--Flinders Street Station and Flagstaff station--are
together driven by the commuters on the work days; however, the former
is overwhelmed by the number of pedestrians during the weekends and
public holidays, compared to the latter. It suggests that Flagstaff
station limits its functionality as simply the public transport hub for
day-to-day commuters, but various activities take place around the
Flinders Street Station other than commuting. Because Flinders Street
Station closely lies to South Bank and other places of attractions where
the locals go for leisure and the tourists for travelling. It can be
noted from Figure \ref{fig:overlay} that State Library follows the
similar temporal trend as Flinders Street Station on non-work days.

@@

\caption[Superimposing line graphs of three sensors in the monthly calendar]{Superimposing line graphs of three sensors in the monthly calendar. The orange line and the purple line, represented by the number of pedestrians at Flagstaff Station and Flinders Street Station, are on top of the green one indicating State Library. Flagstaff station is not as busy as the other two on non-work days.}\label{fig:overlay}
\end{figure}
\end{CodeChunk}

The nighttime events, such as White Night and New Year Evening Firework,
has barely affected the operation of Flagstaff Station but heavily
affected the incoming and outgoing traffic to Flinders Street Station
and State Library on these days.

>>>>

\subsection{Overlaying and faceting
subsets}\label{overlaying-and-faceting-subsets}

The comparison of one sensor to another adds additional insights to the
dataset, which is commonly done with an overlaying plot such as Figure
\ref{fig:overlay}. For instance, the dominant patterns occurred to both
train stations--Flinders Street Station and Flagstaff station--are
together driven by the commuters on the work days; however, the former
is overwhelmed by the number of pedestrians during the weekends and
public holidays, compared to the latter. It suggests that Flagstaff
station limits its functionality as simply the public transport hub for
day-to-day commuters, but various activities take place around the
Flinders Street Station other than commuting. Because Flinders Street
Station closely lies to South Bank and other places of attractions where
the locals go for leisure and the tourists for travelling. It can be
noted from Figure \ref{fig:overlay} that State Library follows the
similar temporal trend as Flinders Street Station on non-work days. The
nighttime events, such as White Night and New Year Evening Firework, has
barely affected the operation of Flagstaff Station but heavily affected
the incoming and outgoing traffic to Flinders Street Station and State
Library on these days.

@@

\caption[Overlaying line graphs of the 3 sensors in the monthly calendar]{Overlaying line graphs of the 3 sensors in the monthly calendar. Flagstaff station is not as busy as the other two on non-work days.}\label{fig:overlay}
\end{figure}
\end{CodeChunk}

As

{\centering \includegraphics[width=\textwidth]{figure/facet-1}

\caption[Line graphs faceted by the 3 sensors in the monthly calendar]{Line graphs faceted by the 3 sensors in the monthly calendar.}\label{fig:facet}
\end{figure}
\end{CodeChunk}
